---
title: "Untitled"
author: "Abigail Gregory"
date: "3/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(gapminder)
install.packages("here")
install.packages("tidyverse")
library(readxl) 
library(haven)
install.packages("svglite")
install.packages("export")
install.packages("ggplot2", dependencies = TRUE)
```


```{r}
(gap_asia_2007 <- gapminder %>% filter(year == 2007, continent == "Asia"))
```






```{r}
write_csv(gap_asia_2007, "exported_file.csv")
```


```{r}
getwd()
```

# just for reference, this code is when youre sharing your code but do not want the attached package to download in case they purposely want a newer or older version.
# {r install, eval=FALSE}



#needed to load "tidyverse" package first
```{r}
write_csv(gap_asia_2007, here::here("data", "s008_data", "exported_file.csv"))
```


```{r}
read_csv(here::here("data", "s008_data", "exported_file.csv"))
```


#recursive = true means make the folders as you go (will make directories along the chain) but flase is only the one at the end. true= "make file path and make all the files you need to make it"
```{r}
dir.create(here::here("data", "s008_data"), recursive = TRUE)


xls_url <- "http://gattonweb.uky.edu/sheather/book/docs/datasets/GreatestGivers.xls"
download.file(xls_url, here::here("data", "s008_data", "some_file.xls"), mode = "wb")
```


```{r}
file_name <- basename(xls_url)
download.file(xls_url, here::here("data", "s008_data", file_name), mode = "wb")
```


```{r}
read_excel(here::here("data", "s008_data", file_name))

```



```{r}
(clevel <- haven::read_spss(here::here("data", "s008_data", "clevel.sav")))

```



# as_factor converts language, gender, and isclevel dbl plus label to factors
```{r}
clevel_cleaned <-
  clevel %>% 
  mutate(language = as_factor(language),
         gender = as_factor(gender),
         isClevel = factor(isClevel, 
                           levels = c(0, 1), 
                           labels = c("No", "Yes"))
  ) %>% 
  print()
```


# Let’s save this file as a CSV file so that it’s a smaller file and easier to import again in the future.


```{r}
write_csv(clevel_cleaned, here::here("data", "s008_data", "clevel_cleaned.csv"))

```



# Now let’s make a plot.

```{r}
clevel_plot <-
  clevel_cleaned %>% 
  mutate(isClevel = recode(isClevel, 
                           No = "Below C-level", 
                           Yes = "C-level"),
         gender = recode(gender,
                         Female = "Women",
                         Male = "Men")) %>% 
  ggplot(aes(paste(isClevel, gender, sep = "\n"), Extraversion, color = gender)) +
  geom_boxplot() +
  geom_jitter(height = .2) +
  scale_color_manual(values = c("#1b9e77", "#7570b3")) +
  ggtitle("Extraversion Stan Scores") +
  scale_y_continuous(breaks = 1:9) %>% 
  print()
```

# Let’s save the plot in several formats. This is useful if we want to use the plot outside of Markdown. Save plots using the ggsave() funnction.

# had to save as jpeg instead of svg because svg was not working 

```{r}
dir.create(here::here("output", "figures"), recursive = TRUE)
ggsave(here::here("output", "figures", "clevel_extraversion.svg"), clevel_plot)
```

